Shannon diversity

### 2021-02-24 analysis/rev_prototyping/additional_metrics_results.Rmd
im tird

That is, e.g. for BBS, the significant deviation is that the observed-to-FS dissimilarity is on average .07 higher than the 95th percentile of FS-to-FS dissimilarity.

@@

<!-- Or we can ask what the difference in dissimilarity scores is on average: -->

<!-- ```{r} -->
<!-- all_di %>% -->
<!--   group_by(singletons, dat) %>% -->
<!--   summarize(mean_actual = mean(mean_po_comparison), -->
<!--             mean_sims = mean(mean_po_comparison_sims), -->
<!--             mean_diff = mean(mean_po_comparison - mean_po_comparison_sims)) -->

<!-- ggplot(filter(all_di), aes(mean_po_comparison_sims, mean_po_comparison, color =  mean_po_comparison_percentile > 95)) + -->
<!--   geom_point() + -->
<!--   facet_wrap(vars(dat)) + -->
<!--   geom_abline(slope = 1, intercept = 0) + -->
<!--   theme(legend.position = "top") -->
<!-- #  -->
<!-- # po_long <- all_di %>% -->
<!-- #   select(dat, singletons, mean_po_comparison, mean_po_comparison_sims) %>% -->
<!-- #   tidyr::pivot_longer(cols = c("mean_po_comparison", "mean_po_comparison_sims"), names_to = "comp", values_to = "val")  %>% -->
<!-- #   mutate(source = ifelse(grepl("sims", comp), "fs_to_fs", "obs_to_fs")) -->
<!-- #  -->
<!-- # ggplot(po_long, aes(source, val)) + -->
<!-- #   geom_boxplot() + -->

<!-- ggplot(filter(all_di), aes( mean_po_comparison - mean_po_comparison_sims)) + -->
<!--   geom_histogram() + -->
<!--   facet_wrap(vars(dat), scales = "free_y") -->

<!-- ``` -->

<!-- ```{r} -->

<!-- ggplot(all_di, aes(mean_po_comparison_sims, mean_po_comparison, color = mean_po_comparison_percentile > 95)) + -->
<!--   geom_point(alpha = .3) + -->
<!--   facet_wrap(vars(dat, singletons)) -->

<!-- ggplot(all_di, aes(mean_po_comparison - mean_po_comparison_sims, color = mean_po_comparison_percentile > 95)) + -->
<!--   geom_histogram(alpha = .3) + -->
<!--   facet_wrap(vars(dat, singletons)) -->

<!-- ``` -->

>>>>

That is, e.g. for BBS, the significant deviation is that the observed-to-FS dissimilarity is on average .07 higher than the 95th percentile of FS-to-FS dissimilarity. I am not 100% sure that this is the best way to make this comparison....

@@

### 2021-02-24 analysis/rev_prototyping/old/shannon.Rmd
im tird

all_di <- all_di %>%
  mutate(log_nparts = log(gmp:::as.double.bigz(nparts)),
         log_nsamples = log(nsamples),
         log_s0 = log(s0),
         log_n0 = log(n0)) %>%
  filter(n0 != s0,
         s0 != 1,
         !singletons,
         n0 != (s0 + 1)) %>%
  mutate(dat = ifelse(grepl(dat, pattern = "fia"), "fia", dat),
         dat = ifelse(dat == "misc_abund_short", "misc_abund", dat)) %>%
  mutate(Dataset = dat,
         Dataset = ifelse(Dataset == "fia", "FIA", Dataset),
         Dataset = ifelse(Dataset == "bbs", "Breeding Bird Survey", Dataset),
         Dataset = ifelse(Dataset == "mcdb", "Mammal Communities", Dataset),
         Dataset = ifelse(Dataset == "gentry", "Gentry", Dataset),
         Dataset = ifelse(Dataset == "misc_abund", "Misc. Abundance", Dataset))

>>>>

all_di <- all_di %>%
  mutate(log_nparts = log(gmp:::as.double.bigz(nparts)),
         log_nsamples = log(nsamples),
         log_s0 = log(s0),
         log_n0 = log(n0)) %>%
  filter(n0 != s0,
         s0 != 1,
         !singletons,
         n0 != (s0 + 1),
         nparts > 20) %>%
  mutate(dat = ifelse(grepl(dat, pattern = "fia"), "fia", dat),
         dat = ifelse(dat == "misc_abund_short", "misc_abund", dat)) %>%
  mutate(Dataset = dat,
         Dataset = ifelse(Dataset == "fia", "FIA", Dataset),
         Dataset = ifelse(Dataset == "bbs", "Breeding Bird Survey", Dataset),
         Dataset = ifelse(Dataset == "mcdb", "Mammal Communities", Dataset),
         Dataset = ifelse(Dataset == "gentry", "Gentry", Dataset),
         Dataset = ifelse(Dataset == "misc_abund", "Misc. Abundance", Dataset))
